Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-06 ms.tex
made it all the way through the bandpass correction discussion

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \verb|i100|/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
therefore computed dimensionless finite bandpass correction factors to 
account for the MBB($\beta$, $T$) spectral shape and the transmission as a 
function of frequency:

\begin{equation}
b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}_{\nu_i}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
\end{equation}

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
adopted the DIRBE bandpass.

The broadband, two-component model prediction in band $\nu_i$, termed 
$\tilde{I}_{\nu_i}$,is then constructed as a linear combination of 
color-corrected MBB terms:

@@

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. This finite bandpass 
correction approach allows us to predict the \textit{broadband} measurement 
$\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the central 
frequency $\nu_{i,c}$ and then multiplying by factors $b_{\nu_i}(T, \beta)$ 
which are interpolated off of a set of precomputed, one-dimensional lookup 
tables. Here the single dimension is $T_k$, as we avoid the necessity of a 
two-dimensional interpolation in both $\beta$ and $T$ by computing a small set 
of one dimensional correction factors for the particular set of $\beta$ values
of interest ($\beta$$\in$\{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}.

% maybe a final sentence to emphasize explicitly that this approach
% is much more computationally feasible than computing integrals
% on-the-fly every time a putative model is proposed (during sampling)

% maybe mention the motivation for computing b_{\nu_i} on a **per MBB**
% basis, the fact that this is more versatile, especially when 
% the ``global parameters'' like f_1 or others are being changed

@@

\subsection{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determines the shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
are sampling the posterior given by:

>>>>

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \verb|i100|/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
therefore computed dimensionless finite bandpass correction factors to 
account for the MBB($T$, $\beta$) spectral shape and the transmission as a 
function of frequency:

\begin{equation} \label{equ:bpcorr}
b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}_{\nu_i}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
\end{equation}

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
adopted the DIRBE transmission curve.

The broadband, two-component model prediction in band $\nu_i$, termed 
$\tilde{I}_{\nu_i}$, is then constructed as a linear combination of 
color-corrected MBB terms:

@@

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. This finite bandpass 
correction approach allows us to predict the \textit{broadband} measurement 
$\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the central 
frequency $\nu_{i,c}$ and then multiplying by factors $b_{\nu_i}(T, \beta)$ 
which are interpolated off of a set of precomputed, one-dimensional lookup 
tables each listing $b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the 
need to interpolate in both $\beta$ and $T$ by computing only a small set of 
one dimensional correction factors for the particular set of $\beta$ values of 
interest ($\beta \in$ \{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}).

This finite bandpass correction approach makes the MCMC sampling described in 
$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
on-the-fly for each proposed dust temperature. We have chosen to compute the 
bandpass corrections on a per-MBB basis because this approach is very 
versatile; all possible two-component models are linear combinations of MBBs, 
so we can apply all of our finite bandpass machinery even when we allow 
parameters other than temperature (e.g. $f_1$) to vary and thereby change the 
dust spectrum shape.

@@

\subsection{Markov Chains}
\label{sec:mcmc}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determines the shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a 
function of the two parameters $T_2$ and $\tilde{I}_{545}$. For each pixel, we 
are sampling the posterior given by:
